Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-07-24 tex/sections/incentive.tex

If an account behaves maliciously, and that behaviour could not have happened due to a mistake, by providing a proof
in a block, the account will be disabled forever in the ARG smart contract. Disabling an account in the
ARG smart contract will prevent that account from signing any valid signature in the future.

Only behaviours will be punished that can not happen due to a mistake or an attack. These behaviours include:
\begin{itemize}
    \item Signing a certificate for a block that is not conditionally valid.
    \item Signing a certificate for two different blocks at the same height if none of them
    is a fork block or a seal block.\footnote{Signing
    a fork block and a normal block at the same height usually is a malicious behaviour. However, it will not be
    penalized because there are circumstances that a honest user could mistakenly do that.}
\end{itemize}

@@

For our incentive mechanism, we require that every time a validator receives a storage page from a PV-DB, after
validating the data, he give a receipt to the PV-DB server. In this receipt the validator signs the
following information:

@@

To incentivize PV-DB servers, a lottery will be held every round,\footnote{A round is the time interval between
two consecutive blocks.} and a predefined amount of ARGs from
\texttt{dbFeeSink} account will be distributed between winners as a prize. This prize will be divided equally
between all \emph{winning tickets} of the lottery.

>>>>

If an account behaves maliciously, and that behaviour could not have happened due to a mistake, by providing a proof
in a block, the account will be disabled forever in the ARG smart contract. Disabling an account in the
ARG smart contract will prevent that account from signing any valid signatures in the future.

Only behaviours will be punished that can not happen due to a mistake or an attack. These behaviours include:
\begin{itemize}
    \item Signing a certificate for a block that is not conditionally valid.
    \item Signing a certificate for two different blocks at the same height if none of them
    is a fork block or a seal block.\footnote{Signing
    a fork block and a normal block at the same height usually is a malicious behaviour. However, it will not be
    penalized because there are circumstances that an honest user could mistakenly do that.}
\end{itemize}

@@

For our incentive mechanism, we require that every time a validator receives a storage page from a PV-DB, after
validating the data, he gives a receipt to the PV-DB server. In this receipt the validator signs the
following information:

@@

To incentivize PV-DB servers, a lottery will be held every round,\footnote{A round is the time interval between
two consecutive blocks.} and a predefined amount of ARGs from
\texttt{dbFeeSink} account will be distributed between the winners as a prize. This prize will be divided equally
between all \emph{winning tickets} of the lottery.

### 2022-07-24 tex/sections/persistence.tex

A page of the AscEE storage should contain objects that have very similar access pattern. Ideally, when a page is needed
for validating a block, almost all of its objects should be needed for either reading or writing. We prefer
that the objects are needed for the same access type. In other words, the objects of a page are chosen in a way that
for validating a block, we usually need to either read all of them or modify\footnote{and probably read.} all of them.

@@

Pages of the AscEE storage are persisted using \emph{dynamic cryptographic accumulators}. Argennon
has three dynamic cryptographic accumulators: \emph{staking} database, which stores all the data that is associated with
the Argennon consensus protocol. \emph{code} database, which stores the AscEE code area, and \emph{heap} database,
which stores the AscEE heap. The commitment of these three accumulators are included in every block of the Argennon
blockchain. These accumulators, in the Argennon network, are hosted on special database nodes called Publicly
Verifiable Database (PV-DB) servers.
We consider the following properties for a PV-DB:
\begin{itemize}
    \item The PV-DB contains a mapping from a set of keys to a set of values.
    \item Every state of the database has a commitment \(C\).
    \item The PV-DB has a method \((D, \pi) = \text{get}(x)\), where \(x\) is a key and \(D\) is the associated data
    with \(x\), and \(\pi\) is a proof.
    \item A user having \(C\) and \(\pi\) can verify that \(D\) is really associated with \(x\), and \(D\) is not
    altered. Consequently, a user who can obtain \(C\) from a trusted source does not need to trust the PV-DB\@.
    \item Having \(\pi\) and \(C\) a user can compute the commitment \(C'\) for the database in which \(D'\) is
    associated with \(x\) instead of \(D\).
\end{itemize}

>>>>

A page of the AscEE storage should contain objects that have very similar access patterns. Ideally, when a page is needed
for validating a block, almost all of its objects should be needed for either reading or writing. We prefer
that the objects are needed for the same access type. In other words, the objects of a page are chosen in a way that
for validating a block, we usually need to either read all of them or modify\footnote{and probably read.} all of them.

@@

Pages of the AscEE storage are persisted using \emph{dynamic cryptographic accumulators}. Argennon
has three dynamic cryptographic accumulators: \emph{staking} database, which stores all the data that is associated with
the Argennon consensus protocol, \emph{code} database, which stores the AscEE code area, and \emph{heap} database,
which stores the AscEE heap. The commitment of these three accumulators are included in every block of the Argennon
blockchain. These accumulators, in the Argennon network, are hosted on special database nodes called Publicly
Verifiable Database (PV-DB) servers.
We consider the following properties for a PV-DB:
\begin{itemize}
    \item The PV-DB contains a mapping from a set of keys to a set of values.
    \item Every state of the database has a commitment \(C\).
    \item The PV-DB has a method \((D, \pi) = \text{get}(x)\), where \(x\) is a key and \(D\) is the associated data
    with \(x\), and \(\pi\) is a proof.
    \item A user having \(C\) and \(\pi\) can verify that \(D\) is really associated with \(x\), and \(D\) is not
    altered. Consequently, a user who can obtain \(C\) from a trusted source does not need to trust the PV-DB\@.
    \item Having \(\pi\) and \(C\) a user can compute the commitment \(C'\) for the database in which \(D'\) is
    associated with \(x\) instead of \(D\).
\end{itemize}
